A community-maintained standard library of population genetic models

### 2020-05-12 popSimManu.tex

The possibility for error and the importance of careful qualty control
was inadvertantly illustrated during our own development process:
during the final revisions of this paper, we noticed that the
OutOfAfrica\_3G09 model \citep{gutenkunst2009inferring}
had not in fact gone through the QC process.
The subsequent QC process revealed that in fact our implementation
slightly wrong---migration rates had not been set to zero to the European population in the longest-ago time period
when there should have only been a single population.
This error was propagated from the \texttt{msprime} documentation,
code which has been used in a number of other publications.

>>>>

The possibility for error and the importance of careful qualty control
was inadvertantly illustrated during our own development process:
during the final revisions of this paper, we noticed that the
OutOfAfrica\_3G09 model \citep{gutenkunst2009inferring}
had not in fact gone through the QC process.
The subsequent QC process revealed that in fact our implementation
slightly wrong---migration rates had not been set to zero to the European population in the longest-ago time period
when there should have only been a single population.
This error was propagated from the \texttt{msprime} documentation,
where the model was presented as an illustrative example.
A number of studies have been published using copies of
this example code.
